Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-01 presentation-plan/Plan_presentation_monday.tex
More <1990
changed structure presentation, don't think STRIP should be presented as well

@@

\subsection{$<$ 1990 (A)}

\begin{itemize}
	\item STRIPS
\end{itemize}

\subsection{1990 - 2000 (I)}
Choose 3 of these depending on what comes out in the different era's:

Model Checking, search techniques, least commitment - probabilistic planner (BURIDAN), DMCPs, dynamic programming, graphplan

Still need to check papers, but already have a bunch.

\subsection{Introducing the FF planner (I)}

\subsection{2000 - 2005 (A)}

\subsection{FF-Replan (I)}

@@

\section{Compare FF-Replan with RFF (I\&A)}

\subsection{How did FF-Replan inspire (I)}

@@

\section{Is it time to reconsider classical planners (I\&A)}

>>>>

What is a planner? [Will need some more detailing].\\

@@

%\begin{itemize}
%	\item STRIPS \cite{fikes1971strips}
%\end{itemize}
%
%\subsubsection{STRIPS}
%
%STRIPS~\cite{fikes1971strips} is a influential method of defining planning
%problems.
%
%Take for example~\ref{fig:strips}. R is the robot, B and C are two objects at
%places a, b and c. The goal is to achieve the configuration such that B is at
%place k and in which C is not at place c. The robot can move to an object and
%it can push objects to another position.
%
%\begin{figure}[htb]%
%\includegraphics[width=0.8\columnwidth]{strips-example.pdf}%
%\caption{Configuration of objects and robot for example problem (Figure from~\cite{fikes1971strips})}%
%\label{fig:strips}%
%\end{figure}
%
%The goal could be written as
%
%\[(\exists s) [ AT(B,k,s) \land \neg AT(C,c,s) ]\]
%
%If we find an instance of s, the problem is solved.
%
%STRIPS also defines operators. In this instance examples can be \texttt{goto}
%and \texttt{push}.
%
%\begin{description}
%	\item[push(u,x,y)] Robot pushes object \texttt{u} from \texttt{x} to
%		position \texttt{y}
%	\begin{description}
%		\item[Precondition:] $(\exists s) [AT(u,x,s) \land ATR(x,s)]$
%		\item[Delete list:] $\{AT(u,x,s), ATR(x,s)\}$
%		\item[Add list:] $\{AT(u,y,push'(u,x,y,s^*)), ATR(y,push'(u,x,y,s^*))\}$
%	\end{description}
%	\item[goto(x,y)] Robot goes from place \texttt{x} to \texttt{y}
%	\begin{description}
%		\item[Precondition:] $(\exists s) [ATR(x,s)]$
%		\item[Delete list:] $\{ATR(x,s)\}$
%		\item[Add list:] $\{ATR(y,goto'(x,y,s^*))\}$
%	\end{description}
%\end{description}
%
%The initial world model can be described by:
%
%\[
%	s_0 : \{ ATR(a,x_0), AT(B,b,s_0), AT(C,c,s_0) \}
%\]
%
%Besides that there is a global requirement that two blocks cannot be at the
%same position at any time.
%
%\paragraph{Problems}
%
%\begin{itemize}
%	\item How to efficiently store nodes (states) of the
%		world.~\cite{fikes1971strips}
%	\item Arbitrary STRIPS planning problem is a PSPACE complete
%		problem.~\cite{mcallester1991systematic}
%	\item Extremely limited in scope of planning problems and complexity of
%		problems it can solve.~\cite{fikes1994strips}
%	\item When executing a plan in a real environment, the resulting state
%		of the world is often different from the state expected by the
%		planner.~\cite{fikes1994strips}
%\end{itemize}
%
%\paragraph{Strengths}
%
%\begin{itemize}
%	\item Formed the basis for many extensions
%
%\end{itemize}

\subsection{Classical Planners}

\subsection{Planning graphs}

\subsection{Planning as a satisfiability}

\subsection{Heuristic search Planning (HSP)}

\subsection{FF Planner (I)}
Use this: \cite{Hoffmann01theff}

\subsection{Markov Decision Processes}

State what's \cite{monahan1982state} is saying about the state of the art MDPs
in the 1980s.

\section{Planning under uncertainty}

\subsection{FF-replan (I)}

@@

\subsection{Compare FF-Replan with RFF (I\&A)}

\subsection{How did FF-Replan and RFF inspire (I)}

\section{Current state-of-the-art planning algorithms}

@@

\section{Is it time to reconsider classical planners under uncertainty (I\&A)}

\bibliographystyle{plain}
\bibliography{Plan_presentation_monday}
